Impacts of air pollution on investors' moods

### 2022-04-27 outputs/paper/paper.Rmd
add model card

```{r bills5, fig.cap="Regression coefficients and 95% confidence intervals for 47 cities", echo = FALSE, fig.height=36, fig.width=32}
# add figure
include_graphics(here::here("inputs/data/im.jpg"))
```

@@

# Additional details

>>>>

```{r bills5, fig.cap="Regression coefficients and 95% confidence intervals for 47 cities", echo = FALSE, fig.height=36, fig.width=32}
# add figure
include_graphics(here::here("inputs/data/im.jpg"))

@@

## Model Card

• Model Details. Basic information about the model.

- Person or organization developing model

  Simo-Pekka Kiihamäki, Marko Korhonen & Jouni J. K. Jaakkola

- Model date

  21 April 2021

- Model version

  2

- Model type

  Linear regression model

- Paper or other resource for more information

  "Ambient particulate air pollution and daily stock market returns and volatility in 47 cities worldwide"

- Citation details

  Kiihamäki, SP., Korhonen, M. & Jaakkola, J.J.K. Ambient particulate air pollution and daily stock market returns and volatility in 47 cities worldwide. Sci Rep 11, 8628 (2021). https://doi.org/10.1038/s41598-021-88041-w

- License

  Creative Commons Attribution 4.0 International License

- Where to send questions or comments about the model

  contact original authors of the paper "Ambient particulate air pollution and daily stock market returns and volatility in 47 cities worldwide."

• Intended Use. Use cases that were envisioned during development.

- Primary intended uses

  used to examine relationships between concentration of PM2.5 and dailt stock returns for 47 cities.

- Primary intended users

  Simo-Pekka Kiihamäki, Marko Korhonen & Jouni J. K. Jaakkola

- Out-of-scope use cases

  Not applicable

• Factors.

- Relevant factors

  The foreseeable salient factors for which model performance may vary includes the accuracy of the dataset.

- Evaluation factors

  Traffic emissions are treated as confounding factors to adjust the model.

• Metrics. Metrics should be chosen to reflect potential realworld impacts of the model.

- Model performance measures

  Not applicable

- Decision thresholds

  Not applicable

- Variation approaches

  Approaches including confidence intervals

• Evaluation Data. Details on the dataset(s) used for the
quantitative analyses in the card.

- Datasets

  Datasets used to evaluate the model were produced by the original authors,

- Motivation

  These datasets obtain air pollution data, stock returns data, and meteorological data which are needed to run the model.

- Preprocessing

  Omitted and imputed missing values.

• Training Data. May not be possible to provide in practice.
When possible, this section should mirror Evaluation Data.
If such detail is not possible, minimal allowable information
should be provided here, such as details of the distribution
over various factors in the training datasets.

  Not applicable

• Quantitative Analyses

- Unitary results

  The summary effect estimate for PM2.5 based on 47 city specific estimates is -0.012 (95% confidence interval -0.021, -0.003), which is statistically significant at the 5% level.

- Intersectional results

  Not applicable

• Ethical Considerations

  The model did not use any sensitive data. The model did not intended to inform decisions about matters central to human life or flourishing. No risk mitigation strategies were used during model development. Risks present in model usage remain unknown.

• Caveats and Recommendations

  The ideal characteristics of an evaluation dataset for this model would be complete data for air pollution, stock returns, and meteorology from reliable sources.
